Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-03-25 WSSSPE1_report/WSSSPE1_summary_report.tex
Draft for the abstract.

\begin{abstract}
This technical report discusses the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1). ...
\end{abstract}

>>>>

\begin{abstract}
This technical report discusses the First Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE1).  The content
is based on the workshop itself, as documented in a set of
collaborative notes taken during the workshop, including discussion
about the keynote presentations, three themed panels that focus on
papers accepted by the workshop, other discussion, cross-cutting
issues, use cases, and conclusions.  It joins a nascent literature
seeking to understand what drives software work in science and how the
reward systems of science thereby shape the type of software work
undertaken, including the extent to which developers are motivated to
build software for the long-term, for the use of others, and whether
to work collaboratively or separately. Unique perspectives were
captured about issues such as documentation of APIs, software
deployment, and development practices; licenses on software; career
paths for scientific software writers; identifiers for software
through a mechanism such as a Digital Object Identifier or
publications of ``software papers''; drawing on evidence of software
contribution, and impact, recorded in online systems such as source
code repositories like GitHub.  For truly sustainable software there
should be no endpoint, as the software products continue to be used
and useful beyond the single institution, grant, and developer or
development team.

\end{abstract}
